Add Amicus Measures

### 2022-04-08 data-cleaning/06-add-amicus-measures.Rmd
join segment vars close #15

@@

```{r}
walkover$CaseId <-  as.character(walkover$CaseId)
walk_measures <- walkover %>% left_join(brief_info, by = c("case_code" = "Case", "brief_code" = "amicus_id"))

@@

@@

**remove any unneeded columns here before saving**

```{r}
box_write(amicus,
           file_name = "amicus_text_512_measures.csv",
           dir_id = 145990409196)
```

>>>>

# change june v russo to case id = 999999
brief_info <- brief_info %>%
  mutate(Case = ifelse(is.na(Case), "999999", Case))

@@

Join to amicus data

```{r}
walkover$case_code <-  as.character(walkover$case_code)
walk_measures <- walkover %>% left_join(brief_info, by = c("case_code" = "Case", "brief_code" = "amicus_id"))

@@

Remove unnecessary columns

```{r}
final <- amicus %>% 
  select(case, id, brief, brief_party, forgau:sgauo, text) %>% 
  janitor::clean_names()
```

Check

```{r}
final %>% head()
```

@@

```{r}
box_write(final,
           file_name = "amicus_text_clean_512_vars.csv",
           dir_id = 145990409196)
```
